The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-25 exp-resurgence.tex
Start rewriting Airy-Lucas thimble projection argument
Also, add comments from meeting.

%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$. Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
%%for some constant $\lambda' \in \R$. It follows that
%%\begin{align*}
%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
%%\end{align*}
\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
\end{proof}
\color{black}
%
\subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
%
The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
Here, we are thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}. We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}
\end{tikzcd}
\end{center}
and it extends to formal power series by countable linearity:
\begin{align*}
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
\end{align*}
This definition extends straightforwardly to fractional powers of $z$. Observing that   
\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
for every $\rho \in \R \setminus \Z_{\leq 0}$, we define 
\begin{align*}
\borel_\zeta[z^{-\rho-1}] \defeq \frac{\zeta^{\rho}}{\Gamma(\rho+1)}.
\end{align*}
Then, for any $\sigma \in \R \setminus \Z_{\leq 0}$, we can extend by countable linearity to the space $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$ of ``fractionally shifted'' formal power series.
%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

@@

Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain. It turns out that 

@@

%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
%\end{problem}
%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem. \textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
\color{DarkBlue}
\subsection{Bridging the gap between analytic and formal objects}
The spaces $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}. To study Borel summation, however, we also need to take Taylor series expansions around $\zeta = 0$, which cannot be done for all functions in $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$. We need a way to make sure we stay in the subspace where the Taylor series exists.

@@

\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[violet!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill \p circle (0.7mm);
  }
\end{tikzpicture}
\end{center}
For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. The intersection of $\zeta^\rho\,\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho} - 1)$, so it is closed.
\end{proof}
If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$. That means its Laurent series is actually a Taylor series.
\begin{prop}\label{prop:shifted_holo_series}
Under the conditions of Lemma~\ref{lem:shifted_holo_closed}, every function in
\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is the sum of a shifted Taylor series in $\zeta^\rho\,\C\{\zeta\}$.
\end{prop}
\begin{proof}
Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, every function $\varphi \in \zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ is the sum of a shifted Laurent series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta, \zeta^{-1}\}$. The definition of $\singexp{\sigma}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^\sigma |\varphi|$ is bounded on a punctured disk around $\zeta = 0$, which would be impossible if $\series{\varphi}$ included any $\zeta^{\rho-1},\;\zeta^{\rho-2},\;\zeta^{\rho-3}\ldots$ terms. That means $\series{\varphi}$ must belong to $\zeta^\rho\,\C\{\zeta\}$.
\end{proof}

@@

Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
\begin{align*}
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
\end{align*}
along any ray. This, as discussed above, proves the desired result.
\end{proof}
\color{black}
\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\textcolor{orange}{[Explain the contents of the section]}
\subsubsection{Regularity results}
Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}\label{eqn:operator-P}
    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
\end{equation}
where
\begin{enumerate}
\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}
\color{DarkBlue}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill \p circle (0.7mm);
}
\end{tikzpicture}

{\small The domain $\Omega_\alpha$}
\end{center}
\begin{proof}
After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. By Theorem~\ref{translation} and the results of Section~\ref{sec:reg-decay}, the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ is a left-invertible map
\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha). \]
With $\Psi_\alpha = \laplace^\theta_{\zeta, \alpha} \psi_\alpha$, the desired result follows.
\end{proof}
\color{BlueViolet}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
Choose a root $-\alpha$ of $P$ with $\tau_\alpha \in (0, \infty)$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill \p circle (0.7mm);
}
\end{tikzpicture}

>>>>

%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$. Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
%%for some constant $\lambda' \in \R$. It follows that
%%\begin{align*}
%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
%%\end{align*}
\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
\end{proof}
\textcolor{magenta}{[Introduce bare $\widehat{\Omega}$]}
\color{black}
%
\subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
%
The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
Here, we are thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}. We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}
\end{tikzcd}
\end{center}
and it extends to formal power series by countable linearity:
\begin{align*}
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
\end{align*}
This definition extends straightforwardly to fractional powers of $z$. Observing that   
\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
for every $\rho \in \R \setminus \Z_{\leq 0}$, we define 
\begin{align*}
\borel_\zeta[z^{-\rho-1}] \defeq \frac{\zeta^{\rho}}{\Gamma(\rho+1)}.
\end{align*}
Then, for any $\sigma \in \R \setminus \Z_{\leq 0}$, we can extend by countable linearity to the space $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$ of ``fractionally shifted'' formal power series.
%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

@@

\textcolor{Pink}{[Optional section; used in theory of difference equations in the frequency domain]} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain. It turns out that 

@@

%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
%\end{problem}
%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem. \textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}

\subsection{Bridging the gap between analytic and formal objects}
The spaces $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}. To study Borel summation, however, we also need to take Taylor series expansions around $\zeta = 0$, which cannot be done for all functions in $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$. We need a way to make sure we stay in the subspace where the Taylor series exists.

@@

\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[ietcoast!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[ietcoast!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[ietcoast] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
  \node at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill[ietcoast] \p circle (0.7mm);
  }
\end{tikzpicture}
\end{center}
For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. The intersection of $\zeta^\rho\,\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho} - 1)$, so it is closed.
\end{proof}
If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$. That means its Laurent series is actually a Taylor series.
\begin{prop}\label{prop:shifted_holo_series}
Under the conditions of Lemma~\ref{lem:shifted_holo_closed}, every function in
\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is the sum of a shifted Taylor series in $\zeta^\rho\,\C\{\zeta\}$.
\end{prop}
\begin{proof}
Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, every function $\varphi \in \zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ is the sum of a shifted Laurent series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta, \zeta^{-1}\}$. The definition of $\singexp{\sigma}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^\sigma |\varphi|$ is bounded on a punctured disk around $\zeta = 0$, which would be impossible if $\series{\varphi}$ included any $\zeta^{\rho-1},\;\zeta^{\rho-2},\;\zeta^{\rho-3}\ldots$ terms. That means $\series{\varphi}$ must belong to $\zeta^\rho\,\C\{\zeta\}$.
\end{proof}

@@

Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
along any ray. This, as discussed above, proves the desired result.
\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
In Section~\ref{sec:regularity-results}, we will prove Borel regularity of the solutions of a certain class of linear level-$1$ ODEs. Then, in Section~\ref{sec:new-summability-proof}, we will give a new proof of Borel summability of the Poincar\'e frame of solutions. \textcolor{Pink}{[Flavor text added; check over]}
\subsubsection{Regularity results}\label{sec:regularity-results}
Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}\label{eqn:operator-P}
    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
where
\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Transition text]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
%\begin{figure}
\fill[ietcoast!20, bezier bounding box, path fading=radial edge]
  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
\fill[ietcoast] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill[ietcoast] \p circle (0.7mm);
